A quantum parallel Markov chain Monte Carlo

### 2022-07-28 main.tex
figures done

 \begin{figure}[!t]
 	\centering
 	\includegraphics[width=1\linewidth]{searchingFigs.pdf}
 	\caption{[Left] Total number of oracle evaluations required by quantum exponential searching algorithm (QESA) \citep{boyer1998tight} for different numbers of solutions $M$ and search set sizes $N$ from 500 independent simulations each.  Horizontal lines at $\frac{9}{4}\sqrt{N}$ represent upper bounds on expected total number of evaluations to obtain a solution for the $M=1$ problem. [Right] Under the same experimental settings, additional number of oracle evaluations required by fixed-point quantum search (FPQS) algorithm of \citet{yoder2014fixed} compared to QESA.}\label{fig:expo}
 \end{figure}

>>>>

 \begin{figure}[!t]
 	\centering
 	\includegraphics[width=1\linewidth]{searchingFigs.pdf}
 	\caption{[Left] Total number of oracle evaluations required by quantum exponential searching algorithm (Algorithm \ref{alg:expoSearch}) for different numbers of solutions $M$ and search set sizes $N$ from 500 independent simulations each.  Horizontal lines at $\frac{9}{4}\sqrt{N}$ represent upper bounds on expected total number of evaluations to obtain a solution for the $M=1$ problem. [Right] Probabilities of success for the fixed-point quantum search algorithm \citep{yoder2014fixed} for different proportions of solutions $\lambda=M/N$ and selecting different lower bounds $w$ on $M/N$ with error tolerance $\delta^2$. }\label{fig:expo}
 \end{figure}

 \begin{figure}[!t]
	\centering
	\includegraphics[width=0.7\linewidth]{searchComparison.pdf}
	\caption{Total number of oracle evaluations required by fixed-point quantum search (FPQS) \citep{yoder2014fixed} minus total required for quantum exponential searching algorithm (QESA) (Algorithm \ref{alg:expoSearch}) for different numbers of solutions $M$ and search set sizes $N$ from 500 independent simulations each.}\label{fig:comp}
\end{figure}
